Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-09-05 GWLDCII.tex
just a few comments on comments

In Section~\ref{sec GN algorithm} we state an algorithm for constructing the Grassmann necklace of the positroid associated to a Wilson loop diagram (Algorithm~\ref{alg:put GN on WLD}) and prove its correctness (Theorem~\ref{res:alg gives GN}). While it was already possible to construct the Grassmann necklace of a Wilson loop diagram via existing bijections between some of the various combinatorial objects that index the positroid cells, this process was convoluted and involved multiple steps; our algorithm allows us to track directly how each propagator in the Wilson loop diagram contributes to each term in the Grassmann necklace. {\color{violet} Furthermore, the above algorithm allows us to determine that the positroids associated to Wilson loop better. In particular, Corrollary \ref{no coloops} shows that these positroids have no coloops, and gives an exact characterization of their loops.}Many of the technical lemmas required to prove Theorem~\ref{res:alg gives GN} continue to be important in subsequent sections: in particular we have Lemma~\ref{lem sian}, which identifies certain configurations of propagators that must appear in any admissible Wilson loop diagram, and Lemma~\ref{vertex cyclic int lem}, which shows that the pattern of values that a propagator contributes to each term of the Grassmann necklace is both simple and predictable.

@@

 \note{Remember to keep an eye out when proofreading: do we just need the vertices appearing in the GN element to be the same, or do we actually need the functions to match up} \sanote{need functions to match in 4.4}

@@

\begin{figure}
\[
\begin{tikzpicture}[baseline=(current bounding box.east)]
	\begin{scope}
	W' = \drawWLDfragment[12]{3}{0.4} 
	%\drawnumberspartial % use this to debug
	\newnode[left]{1}{i}
	\newnode[below]{4}{j}
	\newnode{5}{}
	\newnode{6}{}
	\newnode{7}{}
	\newnode{8}{}
	\newnode{9}{}
	\newnode{11}{}
	\newnode[right]{12}{l+1}
	\begin{scope}
		\clipcenterarc(0,0)(\startpoint-10:\endpoint+10:\radius)
		\newpropbend{6.3}{8.6}{80}
		\node at (\zero + 7.5*\step:\radius*0.8) {\footnotesize $r$};
		\newprop[midway,left]{5.5}{-4}{}
		\node at (\zero + 3*\step:\radius*0.5) {\footnotesize $p$};
		\newprop[midway]{11.5}{-4}{}
		\node at (\zero + 12.2*\step:\radius*0.7) {\footnotesize $q$};
	\end{scope}
\end{scope}
\end{tikzpicture}
\qquad \qquad
\begin{tikzpicture}[baseline=(current bounding box.east)]
	V' = \begin{scope}
	\drawWLDfragment[12]{3}{0.4} 
	%\drawnumberspartial % use this to debug
	\newnode[left]{2}{m}
	\newnode[below]{4}{j}
	\newnode{5}{}
	\newnode{6}{}
	\newnode{7}{}
	\newnode{8}{}
	\newnode{9}{}
	\newnode{11}{}
	\newnode[right]{12}{l+1}
	\begin{scope}
		\clipcenterarc(0,0)(\startpoint-10:\endpoint+10:\radius)
		\newpropbend{6.3}{8.6}{80}
		\node at (\zero + 7.5*\step:\radius*0.8) {\footnotesize $r$};
		\newprop[midway,left]{5.5}{19}{}
		\node at (\zero + 5.5*\step:\radius*0.5) {\footnotesize $s$};
		\newprop[midway]{11.5}{21}{}
		\node at (\zero + 11.8*\step:\radius*0.8) {\footnotesize $t$};
	\end{scope}
\end{scope}
\end{tikzpicture}
\]
\caption{$W'$ and $V'$ are locally the same between $j$ and $l+1$, so we will have $I_i^W\cap [j,l] = I_m^V\cap[j,l]$ even though $p \neq s$ and $q \neq t$.}\label{fig:locally identical}
\end{figure} \sanote{just checking, we are allowing the first and the last propagators (in the $I_i$ induced ordering) to be different, but not the internal ones?}
\end{rmk}

>>>>

In Section~\ref{sec GN algorithm} we state an algorithm for constructing the Grassmann necklace of the positroid associated to a Wilson loop diagram (Algorithm~\ref{alg:put GN on WLD}) and prove its correctness (Theorem~\ref{res:alg gives GN}). While it was already possible to construct the Grassmann necklace of a Wilson loop diagram via existing bijections between some of the various combinatorial objects that index the positroid cells, this process was convoluted and involved multiple steps; our algorithm allows us to track directly how each propagator in the Wilson loop diagram contributes to each term in the Grassmann necklace. {\color{violet} Furthermore, the above algorithm allows us to determine that the positroids associated to Wilson loop better\note{This sentence has a grammar problem and perhaps as a consequence I don't understand what it is saying}. In particular, Corrollary \ref{no coloops} shows that these positroids have no coloops, and gives an exact characterization of their loops.}Many of the technical lemmas required to prove Theorem~\ref{res:alg gives GN} continue to be important in subsequent sections: in particular we have Lemma~\ref{lem sian}, which identifies certain configurations of propagators that must appear in any admissible Wilson loop diagram, and Lemma~\ref{vertex cyclic int lem}, which shows that the pattern of values that a propagator contributes to each term of the Grassmann necklace is both simple and predictable.

@@

 \note{Remember to keep an eye out when proofreading: do we just need the vertices appearing in the GN element to be the same, or do we actually need the functions to match up} \sanote{need functions to match in 4.4}\note{That's ok though because this remark does give the function matching in that region.}

@@

\begin{figure}
\[
\begin{tikzpicture}[baseline=(current bounding box.east)]
	\begin{scope}
	W' = \drawWLDfragment[12]{3}{0.4} 
	%\drawnumberspartial % use this to debug
	\newnode[left]{1}{i}
	\newnode[below]{4}{j}
	\newnode{5}{}
	\newnode{6}{}
	\newnode{7}{}
	\newnode{8}{}
	\newnode{9}{}
	\newnode{11}{}
	\newnode[right]{12}{l+1}
	\begin{scope}
		\clipcenterarc(0,0)(\startpoint-10:\endpoint+10:\radius)
		\newpropbend{6.3}{8.6}{80}
		\node at (\zero + 7.5*\step:\radius*0.8) {\footnotesize $r$};
		\newprop[midway,left]{5.5}{-4}{}
		\node at (\zero + 3*\step:\radius*0.5) {\footnotesize $p$};
		\newprop[midway]{11.5}{-4}{}
		\node at (\zero + 12.2*\step:\radius*0.7) {\footnotesize $q$};
	\end{scope}
\end{scope}
\end{tikzpicture}
\qquad \qquad
\begin{tikzpicture}[baseline=(current bounding box.east)]
	V' = \begin{scope}
	\drawWLDfragment[12]{3}{0.4} 
	%\drawnumberspartial % use this to debug
	\newnode[left]{2}{m}
	\newnode[below]{4}{j}
	\newnode{5}{}
	\newnode{6}{}
	\newnode{7}{}
	\newnode{8}{}
	\newnode{9}{}
	\newnode{11}{}
	\newnode[right]{12}{l+1}
	\begin{scope}
		\clipcenterarc(0,0)(\startpoint-10:\endpoint+10:\radius)
		\newpropbend{6.3}{8.6}{80}
		\node at (\zero + 7.5*\step:\radius*0.8) {\footnotesize $r$};
		\newprop[midway,left]{5.5}{19}{}
		\node at (\zero + 5.5*\step:\radius*0.5) {\footnotesize $s$};
		\newprop[midway]{11.5}{21}{}
		\node at (\zero + 11.8*\step:\radius*0.8) {\footnotesize $t$};
	\end{scope}
\end{scope}
\end{tikzpicture}
\]
\caption{$W'$ and $V'$ are locally the same between $j$ and $l+1$, so we will have $I_i^W\cap [j,l] = I_m^V\cap[j,l]$ even though $p \neq s$ and $q \neq t$.}\label{fig:locally identical}
\end{figure} \sanote{just checking, we are allowing the first and the last propagators (in the $I_i$ induced ordering) to be different, but not the internal ones?}\note{I think I see the problem here.  When I wrote $(j-1, \ldots, \ell+1)$ I meant the *list* from $j-1$ to $\ell+1$, so in particular $j-1$ and $\ell+1$ are included; it was not meant to be interval notation.  However, since we usually do use something more like interval notation we should write $[j-1, \ell+1]$.}

\end{rmk}
